---
title: "US States"
sidebar: false
format:
  html: default
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE, include = FALSE}

library(dplyr)
library(tidyverse)
library(maps)
library(viridis)

us_states <- map_data("state")

Vaccination_Coverage_among_Health_Care_Personnel <- read.csv("C:/Users/abbyh/Downloads/MSCS 264/Vaccination_Coverage_among_Health_Care_Personnel.csv")
```

```{r, echo = FALSE}

flu_vaccine <- Vaccination_Coverage_among_Health_Care_Personnel |>
  select(Vaccine, Geography, Season, Personnel.Type, Estimate....) |>
  filter(Season == "2020-21", Personnel.Type == "All Health Care Personnel")

flu_vaccine <- flu_vaccine |>
  mutate(Geography = str_to_lower(Geography))
```

```{r, echo = FALSE}

flu_vaccine |>
  right_join(us_states, by = c("Geography" = "region")) |>
  rename(region = Geography) |>
  ggplot(mapping = aes(x = long, y = lat,
                          group = group)) + 
  geom_polygon(aes(fill = Estimate....), color = "black") +
  coord_map() +
  theme_classic() +
  scale_fill_viridis() +
  labs(fill = "Percentage", title = "Percentage of Healthcare Workers with the Influenza Vaccine in 2020-21", caption = "healthdata.gov")
  
```

This plot depicts the estimated percentage of all kinds of healthcare workers who received the Influenza vaccine in 2020-21. The percentage was estimated based on a sample size taken throughout the state. We learn that Oregon, Nevada, and Florida have the lowest influenza vaccination rate at about 70-75%. States such as Colorado, South Dakota, and Massachusetts have above a 95% vaccination rate. There doesn't appear to be any clear geographical trends in Influenza vaccinations.
